### 2015-06-20 narrative/intro.tex
Added people in the personnel.config and institutions.config file. Everyone should check their email/name/spell/affiliations in the file to make sure its correct.
Minor updates

1. Application Intentions.\\
2. Metadata Management (middleware and storage system)\\
3. Pluggable infrastructure for data transformation (storage system)\\
4. Intelligent data mapping to storage/memory hierarchies (middleware and storage system)\\
5. Predictable Performance and resolution tradeoffs\\
6. Data re-generation. (middleware & storage)\\
7. Learning Motifs and data re-organization.\\

@@

The metric we are most intrested in optimizing is time to knowledge. Current
approaches to addressing the I/O bottleneck fall into two broad
categories. Parallel file system approaches that optimize the throughput for
an entire system, and I/O middleware approaches that optimize the
performance of a single application. Both approaches have seen success but
are unlikely to overcome the major obstactles in reaching exascale. Instead
of trying to optimize throughput, we will seek to reduce the time to
knowledge. This is the most significant metric for scientific applications
where the desired outcome is not storing data, but rather executing a
knowledge extraction process on the data. Moreover, we aim to perform the
optimization not for a single application, but rather for workload of a
multi-user multi-application system environment.

@@

>>>>

1. Application Intentions.\\
2. Metadata Management (middleware and storage system)\\
3. Pluggable infrastructure for data transformation (storage system)\\
4. Intelligent (autonomic, application-aware) data mapping to storage/memory hierarchies (middleware and storage system)\\
5. Predictable Performance and resolution tradeoffs\\
6. Data re-generation. (middleware \& storage)\\
7. Learning Motifs and data re-organization.\\

@@

The metric we are most interested in optimizing is time to knowledge. Current
approaches to addressing the I/O bottleneck fall into two broad
categories. Parallel file system approaches that optimize the throughput for
an entire system, and I/O middleware approaches that optimize the
performance of a single application. Both approaches have seen success but
are unlikely to overcome the major obstacles in reaching exascale. Instead
of trying to optimize throughput, we will seek to reduce the time to
knowledge. This is the most significant metric for scientific applications
where the desired outcome is not storing data, but rather executing a
knowledge extraction process on the data. Moreover, we aim to perform the
optimization not for a single application, but rather for workload of a
multi-user multi-application system environment.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../proposal"
%%% End:
